\begin{cnabstract}
随着当今科技发展与国家交通强国相关政策扶持，城市轨道交通已经成为了我国交通运输行业的主力军。城市轨道交通运输能力强、准时性高、速达性高、舒适性高、安全性好、系统运营成本低、污染小的特点在大中型城市中颇具优势，近年来，我国多个城市规划、建设并投入使用城市轨道交通线路，带动区域经济的高速发展，为我国国民经济增速带来了良性循环的效果。
城市轨道交通供电系统作为一种电力系统，在运行中往往难以避免出线故障，因此需为其配置成套的继电保护装置。而在城市轨道交通中主要采用直流牵引供电方式，其供电系统与轨道交通牵引系统存在差异，因此其继电保护方案和设备也存在些许差异。
通过对城市轨道交通供电系统的接线形式进行讨论和分析可设计出典型的主变电所、中压环网、牵引降压混合变电所、降压变电所电气主接线图，进而根据继电保护的要求及整定原则进行相应整定计算，以完成城市轨道交通高压系统、中压系统以及直流部分的继电保护设备选型及相应逻辑图的绘制。
\end{cnabstract}
\vspace{1em}\par 
\cnkeywords{城轨供电系统 ; 继电保护 ; 整定计算 ; 设备选型}
\addtocounter{page}{-1}
\begin{enabstract}
With the current technological advancements and support from national policies related to the development of a strong transportation network, urban rail transit has become a cornerstone of China's transportation industry. Urban rail transit is characterized by its robust transport capacity, high punctuality, rapid accessibility, passenger comfort, safety, low operational costs, and minimal environmental impact, making it a highly advantageous mode of transportation in large and medium-sized cities. In recent years, numerous Chinese cities have planned, constructed, and put into operation urban rail transit lines, driving rapid regional economic growth and contributing to a positive feedback loop for the country's overall economic development.\cite[]{}
The power supply system for urban rail transit, as an electrical system, often encounters inevitable line faults during its operation. Consequently, it requires a comprehensive set of relay protection devices. In urban rail transit, the predominant method of traction power supply is direct current (DC), which differs from the power supply systems in other rail transportation systems. Therefore, the relay protection schemes and equipment for urban rail transit exhibit some differences.
By discussing and analyzing the wiring configurations of the power supply system for urban rail transit, we can design typical electrical connection diagrams for primary substations, medium-voltage ring networks, mixed traction and voltage reduction substations, and voltage reduction substations. Subsequently, based on the requirements and principles of relay protection, we can perform the relevant setting calculations to determine the selection of relay protection equipment for the high-voltage system, medium-voltage system, and DC section of urban rail transit, along with the corresponding logic diagrams.
\end{enabstract}
\vspace{1em}\par
\enkeywords{Urban Rail Transit Power Supply System; Relay Protection; Setting Calculations; Equipment Selection}